An Embedding Framework for Consistent Polyhedral Surrogates

### 2020-03-16 journal/poly-embed.tex
Iterating on Raf's notes back to me.

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{$\implies$: Expand a bit more; you want to give the intuition for the ``show'', i.e., why/how can one show this?}
  \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.  3rd needs another careful pass, e.g., supporting hyperplane at what point?   4th cannot be right since you don't cover all reports $r$}
	\jessie{Intuition: $\implies$: Take the injection given, and show there is a property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$. Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that there a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.  Losses match by considering $\risk{\ell}(\delta_y) = \risk{L}(\delta_y) = \ell(\gamma(\delta_y))_y = L(\varphi(\gamma(\delta_y)))_y$ for all $y \in \Y$. }
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Combining with the above, we now have $\risk{L} = \risk{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though.}
	\jessie{Intuition: $\impliedby$: There are a finite set of full-dimensional level sets, which we enumerate, define a finite property, and take the discrete loss values equal to original loss values at the enumerated points.}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

@@

\section{Embedding properties}\label{sec:embed-props}
\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
\raf{Please fix refs, maybe by removing the duplicates from the appendix}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points.  See Lemma~\ref{lem:embed-defs-equiv} to see an equivalence between the two definitions of embedding.}

\jessie{New Lemma here}
\begin{lemma}\label{lem:embed-defs-equiv}
  \raft{Introduce $L$}
	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ eliciting $\gamma$ such that $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
  \raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.}
	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above}
	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
\end{proof}

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
    \end{enumerate}
    \raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} \jessie{= \{\Gamma_{\varphi(r)} : r \in \R\}} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
  \raft{redundant}
  Let $L$ elicit $\Gamma$.
  If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ eliciting $\gamma$ by Lemma~\ref{lem:embed-defs-equiv}.
  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma.}
  We then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$ (chaining Lemma~\ref{lem:embedded-level-sets-trim} and a corollary of the embedding definition).
  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
  \raft{Why is it nonempty though?}
  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

  \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?  (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete.}
	2 $\Rightarrow$ 1:
	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
	Then by Lemma~\ref{lem:loss-restrict}, $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

@@

	1 $\Rightarrow$ 3: 
	Take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
	As the latter set is equal to $\{\gamma_r : r \in \R\}$, we know each $\theta \in \Theta$ is full-dimensional in the simplex, and as $\gamma$ is non-degenerate, we additionally have $\cup \Theta = \cup_r \gamma_r = \simplex$.
%	\hrule
%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
%	As the risks are equal, this is also true for $\Gamma$.
%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

@@

\begin{theorem}[Theorem 3, but type checked]
	A polyhedral loss $L$ indirectly elicits a finite elicitable property $\gamma$ if and only if $\gamma$ is finite and $L$ embeds a loss $\ell$ eliciting property $\gamma'$ which refines $\gamma$.
\end{theorem}
\begin{proof}
	$\Rightarrow$: 
	Since $L$ is polyhedral, we know it embeds some discrete loss $\ell$ by Theorem~\ref{thm:poly-embeds-discrete}.
	Call $\gamma := \prop{\ell}$, since $L$ embeds $\ell$, we have $L$ indirectly eliciting $\gamma$.
	Moreover, $\gamma$ trivially refines itself.

	$\Leftarrow$:
	This direction is a corollary of Proposition~\ref{prop:calibrated-link-refinement}.

\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
\jessie{This is new from the NeurIPS submission.}
\begin{proposition}\label{prop:calibrated-link-refinement}
	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
\end{proposition}
\begin{proof}
	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.

>>>>

\begin{proposition}\label{prop:embed-bayes-risks}
  A loss $L$ embeds discrete loss $\ell$ if and only if $\risk{L}=\risk{\ell}$.
  % A loss $L:\reals^d\to\reals^\Y$ embeds discrete $\ell:\R\to\reals^Y$ if and only if $\risk{L}=\risk{\ell}$.
\end{proposition}
\begin{proof}
  \raft{$\implies$: Expand a bit more; you want to give the intuition for the ``show'', i.e., why/how can one show this?}
  \raft{$\impliedby$: First 2 sentences are good, but then it fogs up a bit.  3rd needs another careful pass, e.g., supporting hyperplane at what point?   4th cannot be right since you don't cover all reports $r$}
	\jessie{Intuition: $\implies$: Take the injection given and take $\U = \varphi(\R)$.
		Since we embed, the loss values match at these embedding points, and we know the surrogate has no ``strictly better'' report than the embedding, otherwise we would contradict the fact that $L$ embeds $\ell$.  
		At any $p \in \simplex$, suppose $r \in \argmin_{r'} \inprod{\ell{r}}{p}$.
		As $\ell(r) = L(\varphi(r))$, we then have $\inprod{p}{\ell(r)} = \inprod{p}{L(\varphi(r))}$.
	The property $\gamma'$ elicited by $L|_\U$ where $\risk{L} = \risk{L|_\U} = \risk{\ell}$.
	$\impliedby$: We know $\risk{\ell}$ is polyhedral, and classic results (Aurenhammer) show that the projection of the facets of the epigraph of $\risk{\ell}$ form a power diagram on the simplex.  Each cell of this power diagram corresponds to a level set of $\gamma_r$.  A corollary of each level set being a cell in a power diagram is that each $\gamma_r$ is full-dimensional.
	Since each $\gamma_r$ is full-dimensional, we know there is a report $u_r$ such that $u_r \in \Gamma(\tilde p)$ for some $\tilde p \in \inter{\gamma_r}$.
	Moreover, the point $(p, -\inprod{p}{L(u_r)})$ forms a supporting hyperplane of $-\risk{L}$ (and therefore $\risk{\ell}$ as well) if and only if $u_r \in \Gamma(p)$ for $p \in \Gamma_{u_r} = \gamma_r$.  
	Losses match by considering the supporting hyperplanes to the facets of the epigraphs of the Bayes Risks are the same, and the loss values are uniquely determined by the final coordinate by this final coordinate of the supporting hyperplane.}
  Throughout we have $L:\reals^d\to\reals^\Y_+$, $\ell:\R\to\reals^\Y_+$, and define $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Suppose $L$ embeds $\ell$ via the embedding $\varphi$.
%  Let $\Gamma = \prop{L}$ and $\gamma = \prop{\ell}$.
  Letting $\U := \varphi(\R)$, define $\gamma':\simplex \toto \U$ by $\gamma' : p \mapsto \Gamma(p)\cap \U$.
  To see that $\gamma'(p) \neq \emptyset$ for all $p\in\simplex$, note that by the definition of $\gamma$ as the property elicited by $\ell$ we have some $r \in \gamma(p)$, and by the embedding condition~\eqref{eq:embed-loss}, $\varphi(r) \in \Gamma(p)$.
  By Lemma~\ref{lem:loss-restrict}, we see that $L|_{\U}$ (the loss $L$ with reports restricted to $\U$) elicits $\gamma'$ and $\risk{L} = \risk{L|_{\U}}$.
  As $L(\varphi(\cdot)) = \ell(\cdot)$ by the embedding, we have
  \begin{equation*}
    \risk{\ell}(p) = \min_{r \in \R}\inprod{p}{\ell(r)} = \min_{r \in \R}\inprod{p}{L(\varphi(r))} = \min_{u \in \U}\inprod{p}{L(u)} = \risk{L|_\U}(p)~,
  \end{equation*}
  for all $p\in\simplex$.
  Combining with the above, we now have $\risk{L} = \risk{\ell}$.

@@

\begin{proposition}\label{prop:embed-risk-poly}
  A loss $L$ embeds a discrete loss if and only if $\risk{L}$ is polyhedral.
\end{proposition}
\begin{proof}
  \raft{Great.  I'd add the piece about taking representatives (how do we construct the finite property?) though.}
	\jessie{Intuition: $\Leftarrow$: There are a finite set of full-dimensional level sets, which we enumerate.  We then use these enumerated reports to define a finite property (i.e. $u_i \in \Gamma(p) \implies i \in \gamma(p)$), and take the discrete loss values equal to original loss values at the enumerated points.}
  If $L$ embeds $\ell$, Proposition~\ref{prop:embed-bayes-risks} gives us $\risk{L} = \risk{\ell}$, and its proof already argued that $\risk{\ell}$ is polyhedral.
  For the converse, let $\risk{L}$ be polyhedral; we again examine the proof of Proposition~\ref{prop:embed-bayes-risks}.
  The projection of $\risk{L}$ onto $\simplex$ forms a power diagram by Theorem~\ref{thm:aurenhammer} with finitely many cells $C_1,\ldots,C_k$, which we can index by $\R := \{1,\ldots,k\}$.
  Defining the property $\gamma:\simplex\toto\R$ by $\gamma_r = C_r$ for $r\in\R$, we see that the same construction gives us points $u_r \in\reals^d$ such that $u_r \in \Gamma(p) \iff r \in \gamma(p)$.
  Defining $\ell:\R\to\reals^\Y_+$ by $\ell(r) = L(u_r)$, the same proof shows that $L$ embeds $\ell$.
  % The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
  % Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
  % Call the set of full-dimensional cells in this power diagram $F$, and note that $F$ is finite since it defined by a projection of a polyhedral function.
  % For each $f \in F$, there is a distribution $p \in \inter{f}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
  % Pick some $u_f \in \argmin_{u' \in \U}L(u', p)$.
  % The coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u_f)$.
  % Repeat this process for every facet, and denote $\R := \{u_f\}_{f \in F}$.
  % Since $\cup f = \simplex$, and each $f$ isequal to $\Gamma_{u_f}$ for some $u_f \in \reals^d$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% <<<<<<< HEAD
%   For the forward direction, suppose $L$ embeds a discrete loss $\ell$.
%   By Proposition~\ref{prop:embed-bayes-risks}, we know that $\risk{L} = \risk{\ell}$.
%   Since $\ell$ is discrete, $\risk{\ell}$ is polyhedral as the minimum of a finite set of linear functions in $\simplex$. %\raf{do we know? okay, we do---but why?}.
%   Therefore, $\risk{L}$ is polyhedral.
%   The reverse direction follows similarly to the proof of Proposition~\ref{prop:embed-bayes-risks}.
%   Consider, as above, the power diagram induced by projecting $\risk{L}$ onto $\simplex$ corresponding to the level sets of $\Gamma$.
%   Call the set of full-dimensional cells in this power diagram $\U'$, where each $U \in \U'$ corresponds to $\Gamma_u$ for some $u \in \U$.
%   For each $u \in \U'$, there is a distribution $p \in \inter{\Gamma_u}$ such that the supporting hyperplane at $\risk{L}(p)$ is unique.
%   Pick some $u \in \argmin_{u' \in \U}L(u', p)$.
%   As before, the coefficients of the supporting hyperplane of $\risk{L}(p)$ exactly describe the discrete loss $\ell(u)$.
%   Repeat this process for every facet.
%   Since $\cup_{\U'} \Gamma_u = \simplex$, we invoke Proposition~\ref{prop:embed-trim} to note $\Gamma:= \prop{L}$ embeds a finite property $\gamma := \prop{\ell}$, and their loss values match up, since $\ell$ is exactly described by the same supporting hyperplanes for each $p \in \simplex$.
% =======
\end{proof}

@@

\section{Embedding properties}\label{sec:embed-props}
\jessie{Forked from appendix... if we adopt this, we should delete some of the content from the appendix.}
\raf{Please fix refs, maybe by removing the duplicates from the appendix}
\jessie{Commented out entire appendix section for the time being.  All that was there that isn't here is some commentary about positive normal sets.}

While Definition~\ref{def:loss-embed} gives the notion of one \emph{loss} embedding another, we now generalize the notion of one \emph{property} embedding another.
\begin{definition}\label{def:prop-embed}
	A property $\Gamma : \simplex \toto \reals^d$ embeds a property $\gamma:\simplex \toto \R$ if there exists some injective embedding $\varphi:\R \to \reals^d$ such that for all $p \in \simplex$ and $r \in \R$, we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p)$.
	\proposedadd{Moreover, we say a loss embeds a property when it embeds a loss eliciting the property.}
\end{definition}

By condition (ii.) of Definition~\ref{def:loss-embed}, we then have $L$ embedding $\ell$ implies $\prop{L}$ embeds $\prop{\ell}$.
\proposedadd{However, we should observe that this statement is not immediately an ``if and only if'' because property embedding does not capture the requirement of matching losses on embedded points; i.e. that $L(\varphi(r)) = \ell(r)$ for all $r \in \R$.  Lemma~\ref{lem:embed-defs-equiv} shows an equivalence between the two definitions of embedding.}

\jessie{New Lemma here}
\begin{lemma}\label{lem:embed-defs-equiv}
%  \raft{Introduce $L$}
	Let $L : \reals^d \to \reals^\Y_+$ be a loss function.
	If the elicitable property $\Gamma := \prop{L}$ embeds the finite property $\gamma : \simplex \toto \R$, then there is a discrete loss $\ell$ such that $\ell$ elicits $\gamma$ and $L$ embeds $\ell$.
\end{lemma}
\begin{proof}
  \raft{All the important pieces are here, but take it slower.  State $\ell$ as a definition (let $\ell$ be given by...) and show why $L$ embeds it.\jessie{Took another pass but changed technique, adding in this detail.}}
  	Consider a loss $\ell : \R \to \reals_+^\Y$, where $\R$ is the same as range of the property $\gamma$.
    Define $\ell : r \mapsto L(\varphi(r))$, where $\varphi$ is the same embedding given by $\Gamma$ embedding $\gamma$.

    Now, we claim that $L$ embeds $\ell$.
    To see this, consider that Condition (i.) is met by construction of $\ell$.
    Moreover, by Proposition~\ref{prop:embed-bayes-risks}, showing $\risk{L} = \risk{\ell}$ suffices to show that $L$ embeds $\ell$.

    We aim to show that for all $p \in \simplex$, we have $\inf_{u \in \reals^d}{p}{L(u)} (1) = (2) \inf_{r \in \R}{p}{L(\varphi(r))}$, and the equality of risks follows.
    $(1) \leq (2)$ follows from the fact that $\varphi(\R) \subset \reals^d$. 
    Consider that if we did not have $(1) \geq (2)$ for some $p \in \simplex$, then there would be no $r$ such that $\varphi(r) \in \Gamma(p)$, and therefore the property it embeds, $\gamma$ is degenerate at $p$, i.e. $\gamma(p) = \emptyset$, yielding a contradiction.
    Therefore, we must have $\risk{L} = \risk{\ell}$.

    Now, to verify $\ell$ elicits $\gamma$, consider $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

%    \hrule
%	If $\Gamma$ embeds a finite $\gamma$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$ for all $r \in \R$.  
%	Moreover, we can see $\ell$ elicits $\gamma$ since we have $r \in \gamma(p) \iff \varphi(r) \in \Gamma(p) \iff \varphi(r) \in \argmin_{u \in \reals^d} \inprod{p}{L(u)} \iff r \in \argmin_{r \in \R} \inprod{p}{\ell(r)}$.

  \raft{Spell this out; I don't think these distributions are enough, for the same reason as above.  \jessie{Took a different approach of using Prop 1 to show the risks are equal.}}
%	The final condition of matching loss values is satisfied by considering the equality of the expected loss on each $\delta_y$ distribution.
\end{proof}

@@

\begin{proposition}\label{prop:embed-trim}
	Let $\Gamma:\simplex\toto\reals^d$ be an elicitable property.
	The following are equivalent:
	\begin{enumerate}\setlength{\itemsep}{0pt}
		\item $\Gamma$ embeds a finite property $\gamma:\simplex \toto \R$.
		\item $\trim(\Gamma)$ is a finite set, and $\cup\,\trim(\Gamma) = \simplex$.
		\item There is a finite set of full-dimensional level sets $\Theta$ of $\Gamma$, and $\cup\,\Theta = \simplex$.
    \end{enumerate}
    %\raft{I see why you wanted this addition here, but (a) it's clear from the def of embedding, and (b) we don't have varphi defined.  So let's leave it out.}
	Moreover, when any of the above hold, $\{\gamma_r : r\in\R\} = \trim(\Gamma) = \Theta$, and $\gamma$ is elicitable.
\end{proposition}
\begin{proof}
	Let $L$ elicit $\Gamma$.

	1 $\Rightarrow$ 2:
        %\jessie{Loss intuition: Let $L$ elicit $\Gamma$.  If $\Gamma$ embeds a finite $\gamma'$, $L$ must embed a discrete loss $\ell$ such that $\ell(r) = L(\varphi(r))$.  Therefore, $\risk{L} = \risk{\ell}$ is polyhedral. Moreover, we have $\Gamma$ also embedding the finite property $\prop{\ell} := \gamma$ as a corollary of the definition of embedding properties. We claim $\trim(\Gamma) = \{\gamma_r : r \in \R\}$ (Lemma~\ref{lem:embedded-level-sets-trim}), and since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.  Moreover, as $\gamma$ is nondegenerate (since it is defined over the simplex), we have that $\cup_{r \in \R} \gamma_r = \simplex$.}
  If $\Gamma$ embeds a finite $\gamma$, then Lemma~\ref{lem:embed-defs-equiv} says there is be a discrete loss $\ell$ embedded by $L$ such that $\ell$ elicits $\gamma$.
  \raft{Again, a bit too brief.  Consider adding some of this statement into the Lemma. \jessie{Is this better?}}
  by Lemma~\ref{lem:embedded-level-sets-trim}, we then observe that $\trim(\Gamma) = \{\Gamma_{\varphi(r)} : r \in \R \} = \{\gamma_r : r \in \R\}$.
%  \raft{Replace with ``As $\R$ is finite, we conclude $\trim(\Gamma)$ is finite.'' or similar}
  As $\R$ is finite, we conclude that $\trim(\Gamma)$ is also finite.
%  Since the latter set is finitely generated (as $\R$ is finite), we have have $\trim(\Gamma)$ is finite.
  \raft{Why is it nonempty though?  \jessie{Just above definition 2, we specify that properties are nonempty}}
  Moreover, as $\gamma$ is nondegenerate (recall that $\gamma: \simplex \toto \R$ is shorthand for $\gamma: \simplex \to 2^\R \setminus \emptyset$), we have that $\cup \trim(\Gamma) = \cup_{r \in \R} \gamma_r = \simplex$.

  \raft{These next two directions together seem like what we did before for $2\Rightarrow 3$, correct?  (Not as complete though; see the step where we justify the conditions of Lemma~\ref{lem:loss-restrict}.)  I'm actually happy for them to be separated, but let's make sure the argument is just as complete. \jessie{Added in the conditions of Lemma 3 to be a bit more thorough.}}
	2 $\Rightarrow$ 1:
	As $\trim(\Gamma)$ is finite, we know $\trim(\Gamma) = \{\Gamma_{u_i}\}_{i=1}^k$ for some finite $k$.
	Take $\U = \{u_1, \ldots, u_k\}$, and consider $L$ eliciting $\Gamma$ and $\ell := L|_{\U}$.  
	We have $\U \subset \reals^d$ and $\Gamma(p) \cap \U \neq \emptyset$ for all $p$, since we have $p \in \Gamma_{u_i}$ for some $u_i \in \U$.
	Then we can apply Lemma~\ref{lem:loss-restrict} to observe that $L$ embeds $\ell$, and therefore $\Gamma$ embeds $\prop{\ell}$, which is finite as $\ell$ is discrete.

@@

	1 $\Rightarrow$ 3: 
	Let $\varphi: \R \to \reals^d$ by the embedding function, and take $\Theta = \{\Gamma_{\varphi(r)} : r \in \R\}$.
	The latter set is equal to $\{\gamma_r : r \in \R\}$ by $\Gamma$ embedding $\gamma$.
	Therefore, we know each $\theta \in \Theta = \gamma_r$ for some $r \in \R$, which is full-dimensional in the simplex.
	Moreover, since $\gamma$ is non-degenerate, we have $\cup \Theta = \cup_r \gamma_r = \simplex$.
%	\hrule
%	Since $\Gamma$ embeds the finite property $\gamma$, Lemma~\ref{lem:embed-defs-equiv} yields a loss $\ell$ eliciting $\gamma$ embedded by $L$, and therefore $\risk{L} = \risk{\ell}$.
%	As in the proof of Proposition~\ref{prop:embed-bayes-risks}, we observe that every facet of the epigraph of $-\risk{\ell}$ projects onto the simplex as a full-dimensional level set of $\gamma$.
%	As the risks are equal, this is also true for $\Gamma$.
%	Observe each cell in the simplex of $\gamma$ has some report $r$ so the cell is $\gamma_r$.
%	If $\varphi: r \mapsto u_r$, then we must have $\gamma_r = \Gamma_{u_r}$.
%	Take $\Theta$ to be the set $\{\Gamma_{u_r} : u_r \in \varphi(\R)\}$.
%	We have shown each $\Gamma_{u_r}$ is full-dimensional, and as the union of these cells forms a power diagram on $\simplex$, we have $\cup \Theta = \simplex$.

@@

\iffalse
\jessie{Other results on refined properties? Assuming we don't want the embedding dimension conjecture brought up on 02.03.2020 in here.}
\jessie{This is new from the NeurIPS submission.}
\begin{proposition}\label{prop:calibrated-link-refinement}
	Take $\prop{\ell} =: \gamma : \simplex \toto \R$ and $\prop{\ell'} =:\gamma' : \simplex \toto \R'$.
	If $\gamma'$ refines $\gamma$ and $L'$ is calibrated with respect to  the discrete loss $\ell'$, then there exists a link $\psi$ so that $(L', \psi)$ is calibrated with respect to $\ell$.
	\proposedadd{$(L, \psi)$ calibrated w.r.t. $\ell \implies L $ indirectly elicits $\prop{\ell}$.}
\end{proposition}
\begin{proof}
	Let us construct the link $\psi$ such that, for all $r' \in \R'$ consider $r \in \R$ so that $\gamma'_{r'} \subseteq \gamma_r$.
	Define $\psi$ so that $\psi'(u) = r' \implies \psi(u) = r$.
